\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2014-06-12 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
added a link to the developers' wiki

>>>>

\section{Becoming a developer of the code, or making small modifications in the source code}

If you want to develop new features in the code, and/or if you want to make small changes, improvements, or bug fixes, you are very welcome to contribute. To do so, i.e. to access the development branch of the source code with read/write access (in a safe way, no need to worry too much about breaking the package, there is a robot called BuildBot that is in charge of checking and validating all new contributions and changes), please visit this Web page: \url{https://github.com/geodynamics/specfem3d/wiki/Using-Hub}.
